### 2012-03-27 exam4/2.tex
done with soln

\emph{Good luck!}
\end{minipage}\hfil\begin{minipage}[t]{6cm}
\rule{1cm}{0pt}\begin{tabular}{|c|l|@{/}r|}
\hline
{\bf Problem} & Points & out of \\ \hline
1 & & 15\\ \hline
2 & & 22\\ \hline
3 & & ??\\ \hline
4 & & ??\\ \hline
5 & & ??\\ \hline
%% Extra & & 5 \\ \hline
{\bf Total} & & ?? \\ \hline
%{\bf Base}  & \multicolumn{2}{l|}{{\bf 56}} \\ \hline
\end{tabular}
\end{minipage}

@@

//> 3pts for tests
t3.height -> 4
r.height -> 1
t2.height -> 3
\end{verbatim}
\end{solution}
\end{problem}
%\ifrubric\bigskip\else
\newpage
%\fi

@@

@@

\begin{problem}
\pts{???}

@@

\begin{solution}
\begin{verbatim}
class RangeIterator implements Iterator<Integer> {
  Integer lo;
  Integer hi;

@@

  Boolean hasNext() { return this.lo <= this.hi; }

  Integer next() { this.lo = this.lo + 1; return this.lo - 1; }
}

// Tests
RangeIterator ri = new RangeIterator(0,2);
ri.hasNext() -> true
ri.next() -> 0
ri.next() -> 1
ri.hasNext() -> true
ri.next() -> 2
ri.hasNext() -> false
\end{verbatim}
\end{solution}
\newpage

@@

\ifrubric
\begin{solution}
\begin{verbatim}
class Square implements Function<Integer,Integer> {
  Integer call(Integer x) { return x * x; }
} 
Square s = new Square();
s.call(3) -> 9
s.call(0) -> 0
\end{verbatim}
\end{solution}
\else
\newpage
\fi

@@

\ifrubric
\begin{solution}
\begin{verbatim}
class MapIterator<T,U> implements Iterator<U> {
  Function<T,U> f;
  Iterator<T> i;
  MapIterator<T,U>(Function<T,U> f, Iterator<T> i) {
   this.f = f; this.i = i;
  }

  boolean hasNext() { return i.hasNext(); }
  U next() { return f.call(i.next()); }
}

//tests
Iterator<Integer> i = new MapIterator<Integer,Integer>(new Square(), 
                           new RangeIterator(1,5));
i.next() -> 1
i.next() -> 4
i.next() -> 9
i.hasNext() -> true

@@

\ifrubric
\begin{solution}
\begin{verbatim}
class Test {
  Integer sumSquares(Integer a, Integer b) {
    Iterator<Integer> i = new MapIterator<Integer,Integer>(new Square(), 
                             new RangeIterator(a,b));
    Integer sum = 0;
    while (i.hasNext()) { sum += i.next(); }
    return sum;
  }
}

sumSquares(1,2) -> 5
sumSquares(0,0) -> 0
sumSquares(10,10) -> 100
\end{verbatim}
\end{solution}
\else
\newpage
[Here is some more space for the previous problem.]
\fi

>>>>

\emph{Good luck!}
\end{minipage}\hfil\begin{minipage}[t]{6cm}
\rule{1cm}{0pt}\begin{tabular}{|c|l|@{/}r|}
\hline
{\bf Problem} & Points & out of \\ \hline
1 & & 15\\ \hline
2 & & 22\\ \hline
3 & & ??\\ \hline
4 & & ??\\ \hline
5 & & 20\\ \hline
%% Extra & & 5 \\ \hline
{\bf Total} & & ?? \\ \hline
%{\bf Base}  & \multicolumn{2}{l|}{{\bf 56}} \\ \hline
\end{tabular}
\end{minipage}

@@

//> 3pts for tests
t3.height() -> 4
r.height() -> 1
t2.height() -> 3
\end{verbatim}
\end{solution}
\end{problem}
%\ifrubric\bigskip\else
\newpage
%\fi

@@

// in Tree:
  <T> T visit(TreeVisitor<T> v);

@@

\begin{problem}
\pts{20}

@@

\begin{solution}
\begin{verbatim}
//> 4pts
class RangeIterator implements Iterator<Integer> {
  Integer lo;
  Integer hi;

@@

  public boolean hasNext() { return this.lo <= this.hi; }

  public Integer next() { this.lo = this.lo + 1; return this.lo - 1; }
}

//> Tests 2pts
RangeIterator ri = new RangeIterator(0,2);
ri.hasNext() -> true
ri.next() -> 0
ri.next() -> 1
ri.hasNext() -> true
ri.next() -> 2
ri.hasNext() -> false
\end{verbatim}
\end{solution}
\newpage

@@

\ifrubric
\begin{solution}
\begin{verbatim}
//> 3pts
class Square implements Function<Integer,Integer> {
  public Integer call(Integer x) { return x * x; }
} 
Square s = new Square();
s.call(3) -> 9
s.call(0) -> 0
\end{verbatim}
\end{solution}
\else
\newpage
\fi

@@

\ifrubric
\begin{solution}
\begin{verbatim}
//> 4pts
class MapIterator<T,U> implements Iterator<U> {
  Function<T,U> f;
  Iterator<T> i;
  MapIterator<T,U>(Function<T,U> f, Iterator<T> i) {
   this.f = f; this.i = i;
  }

  public boolean hasNext() { return i.hasNext(); }
  public U next() { return f.call(i.next()); }
}

//tests 2pts
Iterator<Integer> i = new MapIterator<Integer,Integer>(new Square(), 
                           new RangeIterator(1,5));
i.next() -> 1
i.next() -> 4
i.next() -> 9
i.hasNext() -> true

@@

\ifrubric
\begin{solution}
\begin{verbatim}
//> 4pts
class Test {
  Integer sumSquares(Integer a, Integer b) {
    Iterator<Integer> i = new MapIterator<Integer,Integer>(new Square(), 
                             new RangeIterator(a,b));
    Integer sum = 0;
    while (i.hasNext()) { sum += i.next(); }
    return sum;
  }
}

//> Tests 1pt
sumSquares(1,2) -> 5
sumSquares(0,0) -> 0
sumSquares(10,10) -> 100
\end{verbatim}
\end{solution}
\else
\newpage
[Here is some more space for the previous problem.]
\fi
